% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{\href{http://svr6.haohaizi.us/}{\LARGE ZHANG Xiao}} & \href{mailto:zx0319@gmail.com}{Mail:zx0319@gmail.com} Tel:13609206315\\
	{\footnotesize \texttt{{[Birth: Mar.1991]}}} & \href{https://cn.linkedin.com/pub/xiao-zhang/51/13/6a8}{https://cn.linkedin.com/pub/xiao-zhang/51/13/6a8} \\
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
	\begin{itemize}
		\item
			\ressubheading{\href{http://www.xjtu.edu.cn}{Xi'an Jiaotong University}}{Xi'an,China}{\href{http://www.cs.xjtu.edu.cn}{Master Degree of Computer Science-GPA:86.42/100};}{Sep. 2013 -- Jun.2017 }
		\item
			\ressubheading{\href{http://www.xjtu.edu.cn}{Xi'an Jiaotong University}}{Xi'an,China}{\href{http://www.cs.xjtu.edu.cn}{Bachelor Degree of Computer Science-GPA:85.69/100};}{Sep. 2009 --  Jun.2013}
		\item
			\ressubheading{\href{http://www.cuhk.edu.hk}{The Chinese University of Hong Kong}}{Hong Kong,China SAR}{{International Exchange Student Program-GPA:3.675/4.0};}{Jan. 2012 -- Jun. 2012}
	\end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Internship Experience}
	\begin{itemize}
		\item 
			\ressubheading{Cloud Analytics and Service Team}{IBM China Research Laboratory}{Research Assistant Intern}{Jul. 2015 -- N O W}
				{ \footnotesize
				\begin{itemize}
					\resitem{Lead by IBM regular research member Fanjing Meng and Sr.manager Jingming Xu;}
					\resitem{Research on distinguish malicious or abnormal process using machine learning technology;}
					\resitem{Research on the cutting edge docker framework--kubernetes, and enhance the scheduler to make it architecture-aware;}
					\resitem{Design and develop a prototype to exploit common patterns and debug framework in commercial database.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://nskeylab.xjtu.edu.cn/}{NSkeyLab of the Ministry of Education}}{Xi'an Jiaotong University}{Software Engineer}{Jun. 2010 -- Aug. 2010}
				{ \footnotesize
				\begin{itemize}
					\resitem{Develop and package some virtualized development environment;}
					\resitem{Manage and maintain some Linux servers.}
				\end{itemize}
				}

	\end{itemize}
	
\resheading{Research Project}
	\begin{itemize}
		\item 
			\ressubheading{Database Drift Pattern Analyzer}{IBM China Research Laboratory}{Cloud Analytics and Service Team}{Jul. 2015 -- N O W}
				{ \footnotesize
				\begin{itemize}
					\resitem{Focus the changing pattern in commercial database;}
					\resitem{Patterns includes data schema, keys and related property;}
					\resitem{Develop the drift collecting module;}
					\resitem{Develop the suffix tree algorithm to exploit the common pattern;}
					\resitem{Related patent is under review.}
				\end{itemize}
				}
		\item 
			\ressubheading{Anomaly Detection at Process in Cloud}{IBM Research China}{Cloud Analytics and Service Team}{Jul. 2015 -- N O W}
				{ \footnotesize
				\begin{itemize}
					\resitem{Focus the processes in cloud environment;}
					\resitem{Take multi-process and multi-thread into consideration;}
					\resitem{Improve the drift collecting module;}
					\resitem{Adapt machine learning method to recognize the common process pattern;}
					\resitem{Related patent is under review.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://eiegrd.xjtu.edu.cn/}{The Long Tail in Application Consolidation in Data Center}}{Xi'an Jiaotong University}{The Institution of Computer Software and Theory}{Sep. 2014 -- Feb. 2015}
				{ \footnotesize
				\begin{itemize}
					\resitem{Focus on fully utilizing hardware performance of data center;}
					\resitem{Research on the reasons of long tail in OS events level;}
					\resitem{Profile the system events sequence under long tail, and train the sequence as Markov chain.}
				\end{itemize}
				}
		\item 
			\ressubheading{\href{http://eiegrd.xjtu.edu.cn/}{VRAM Re-allocation of Virtual Machine Monitor}}{Xi'an Jiaotong University}{The Institution of Computer Software and Theory}{Mar. 2013 -- Aug. 2013}
				{ \footnotesize
				\begin{itemize}
					\resitem{Investigate on the VRAM allocation of self-crafted Virtual Machine Monitor;}
					\resitem{Research on the Linux boot RAM space;}
					\resitem{Use AMD nested paging instruction set.}
				\end{itemize}
				}
	\end{itemize}

%\resheading{Industrial Project}
%	\begin{itemize}
%		\item 
%			\ressubheading{EATON Kanban Visual System}{EATON Inc}{Develop Architect and Test}{May. 2014 -- Dec. 2014}
%				{ \footnotesize
%				\begin{itemize}
%					\resitem{Deploy Django framework;}
%					\resitem{Deploy Python and Django in EATON IT system;}
%					\resitem{Implement BootStrap responsive UI framework;}
%					\resitem{Adjust Windows Server 2008R2 ,SQL Server 2012 and IIS environment;}
%					\resitem{Cooperate with EATON on checking in Apple iPad and 4K LED TV(SAMSUNG+Android Driver Terminal);}
%					\resitem{Infer Django object model from SAP sub table schema automatically;}
%				\end{itemize}
%				}
%		\item 
%			\ressubheading{OPAC Book Search Engine and QR Integration}{The library of Xi'an Jiaotong University}{Develop Architect and Test}{Apr. 2014 -- Jun. 2015}
%				{ \footnotesize
%				\begin{itemize}
%					\resitem{Implement the cloud service and integrate with VMWare;}
%					\resitem{Install \& configure infrastructure;}
%					\resitem{Investigate Open-Source QR code;}
%					\resitem{Implement B/S QR generating API;}
%					\resitem{Integrate QR generating API with OPAC Book Search Engine;}
%					\resitem{Deploy with official name server;}
%					\resitem{参与图书情报学中文核心期刊论文的撰写;}
%					\resitem{http://git.0ydy.com/qlib/qrlib-server}
%				\end{itemize}
%				}
%	\end{itemize}		

\resheading{Scholarship}
	\begin{itemize}
		\item
			IBM Fellowship of the year 2016-2017 (1of 5 candidates in China Mainland), IBM, 2016
		\item
			PengKang Scholarship (limited to Top 5\%), Xi'an Jiaotong University, 2012
		\item
			SiYuan Scholarship (limited to Top 15\%), Xi'an Jiaotong University, 2011
		\item
			SiYuan Scholarship (limited to Top 15\%), Xi'an Jiaotong University, 2010
	\end{itemize}

\resheading{Awards}
	\begin{itemize}
		\item
			National 2nd Award in IBM Smart Earth- IoT Contest, IBM, 2014
		\item
			Excellent Award of China Northwest Region in Tencent WeChat Public Platform Development Contest, Tencent, 2013
		\item
			Outstanding Graduate, Xi'an Jiaotong University, 2013
		\item
			Excellent Bachelor Graduation Thesis (Limited to Top 1\%), 2013
	\end{itemize}
	

	

%%%%%%%%%%%%%%%%%%%%%%


\resheading{Publication and Patent}
	\begin{itemize}
		\item
			Meng, F., \textbf{Zhang, X.}, Chen, P., \& Xu, J. (2017, June). DriftInsight: Detecting Anomalous Behaviors in Large-scale Cloud Platform. In Cloud Computing (CLOUD), 2017 IEEE 10th International Conference on (pp. 917-920). IEEE.
		\item
			\textbf{Zhang, X.}, Meng, F., Chen, P., \& Xu, J. (2016, June). TaskInsight: A fine-grained performance anomaly detection and problem locating system. In Cloud Computing (CLOUD), 2016 IEEE 9th International Conference on (pp. 917-920). IEEE.
		\item
			Meng, F. J., Wegman, M. N., Xu, J. M., \textbf{Zhang, X.}, Chen, P., \& Chafle, G. (2017). IT troubleshooting with drift analysis in the DevOps era. IBM Journal of Research and Development, 61(1), 6-62.
		\item
			Cheng, Y., \textbf{Zhang, X.}, Wang, P., Zha, L., Hou, D., Qi, Y., \& Ma, C.. (2017). Data Management Challenges and Event Index Technologies in High Energy Physics. Journal of Computer Research and Development[Chinese], 54(2), 258-266.
		\item
			Method and System for State-based Misbehavioring System Detection, 2017, U.S. Patent Agency
		\item
			Method for Transaction Discovery in Log Sequence, 2016, U.S. Patent Agency
		\item
			AppRadar: A Touchless and Lightwerght Application Discovery Approach in the Cloud, 2016, U.S. Patent Agency
		\end{itemize}

\resheading{Skills}
	\begin{description}
		\item[Languages:] { \footnotesize C/C++,Python}
		\item[Software:]{\footnotesize {iPython Notebook};{sklearn};{scipy};{numpy}}  
		\item[English:]{ TOEFL 106 (L28, S22; R29; W27); GRE 320 (V152; Q168; AW3.5)}
	\end{description} % End Skills list

\end{document}
